---
title: "CLT"
author: "Jake Glickman"
date: '2022-06-08'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
origmean <- mean(my1000)
origsd <- sd(my1000)
options(digits = 1)
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 


The mean of the original plot is `r origmean` and the standard deviation is `r origsd`.


Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
sample2mean <- mean(x.avg)
sample2sd <- sd(x.avg)
```

This plot is not unimodal. It has three peaks, two of which are the same size and one larger peak in the middle. This is due to the plot showing the average of votes. The average mean with 2 samples is `r sample2mean` and the standard deviation is `r sample2sd`.

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
sample4mean <- mean(x.avg)
sample4sd <- sd(x.avg)
```

The mean with 4 samples is `r sample4mean` and the standard deviation is `r sample4sd`.


```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
sample9mean <- mean(x.avg)
sample9sd <- sd(x.avg)
```

The mean with 9 samples is `r sample9mean` and the standard deviation is `r sample9sd`.


```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
sample16mean <- mean(x.avg)
sample16sd <- sd(x.avg)
```

The mean with 16 samples is `r sample16mean` and the standard deviation is `r sample16sd`.


```{r}
numb = 25
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 25")
sample25mean <- mean(x.avg)
sample25sd <- sd(x.avg)
```

The mean with 25 samples is `r sample25mean` and the standard deviation is `r sample25sd`.


```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
sample36mean <- mean(x.avg)
sample36sd <- sd(x.avg)
```

The mean with 36 samples is `r sample36mean` and the standard deviation is `r sample36sd`.


